---
title: "clean_to_processed_data_code"
format: html
---

# Researcher burnout and questionable research practice pilot data analysis

## Descriptive analysis

### Load libraries

```{r echo = FALSE ouput = FALSE}
library(tidyverse)
library(here)
library(ggplot2)
data_path <- here("data")
```

### Load data

```{r echo = FALSE ouput = FALSE}
data = read_csv(here::here("data/aggregated_data.csv"))
```

# General participant statistics

## Number of participants

```{r}
n = data |> 
  summarise(n = n())
```

## Gender

```{r}
gender = data |> 
  group_by(gender) |> 
  summarise(n = n())
```

## Title

```{r}
title = data |> 
  group_by(title) |> 
  summarise(n = n())
```

## Discipline

```{r}
discipline = data |> 
  group_by(discipline) |> 
  summarise(n = n())
```

## Most recent article published

```{r}
last_published = data |> 
  group_by(last_published) |> 
  summarise(n = n())
```

## Academic career length

```{r}
academia_length = data |> 
  group_by(academia_length) |> 
  summarise(n = n())
```

## PhD

```{r}
phd = data |> 
  filter(title == "PhD student") |> 
  group_by(phd_dissertation) |> 
  summarise(n = n())
```

# Survey statistics

## Distribution

```{r}
library(rlang)

survey = c("burnout", "influence", "meaning", "opportunities", "social_support", "workload",
           "general_satisfaction", "open_practice", "pay_satisfaction", "tool_satisfaction",
           "qrp_attitude", "role_conflict", "role_ambiguity", "pub_pressure_stress",
           "pub_pressure_attitude", "pub_pressure_resource")


distribution = function(data, survey){
  var = sym(survey)
  
  data |>
  ggplot(aes(x = !!var)) +
  geom_bar()

  ggsave(paste0("figures/", survey, "_distribution.png"))
}

for (i in survey){
  assign(paste0(i, "_distribution"), distribution(data, i))
}

#Introduce range based on survey min and max
```

## Deeper look at QRP attitude scale

### As other scales are validated and reliable, we will focus on QRP attitude scale

```{r}
processed = read_csv(here::here("data/processed_data.csv"))
qrp_data = processed |> 
  select(anonym_id, qrp_attitude_1:qrp_attitude_8) |> 
  left_join(select(data, anonym_id, qrp_attitude), by = "anonym_id")

#Distribution for each question

qrp_questions = c("qrp_attitude_1", "qrp_attitude_2", "qrp_attitude_3", "qrp_attitude_4",
                  "qrp_attitude_5", "qrp_attitude_6", "qrp_attitude_7", "qrp_attitude_8")

qrp_distribution_function = function(data, question){
  var = sym(question)
  
  data |>
  ggplot(aes(x = !!var)) +
  geom_bar() +
  coord_cartesian(xlim = c(1, 5))
  
  ggsave(paste0("figures/qrp/", question, "_distribution.png"))
}

for (i in qrp_questions){
  assign(paste0(i, "_distribution"), qrp_distribution_function(qrp_data, i))
}

#Correlation between questions

correlation = qrp_data |> 
  select(qrp_attitude_1:qrp_attitude_8) |> 
  cor(use = "complete.obs")

#Check floor effects
## Floor effects are present when more than 30% of the participants score the lowest possible score (researcher decision)
floor_effects = qrp_data |> 
  select(qrp_attitude_1:qrp_attitude_8) |> 
  summarise_all(~sum(.x == 1, na.rm = TRUE)/n()) |>
  pivot_longer(cols = everything(), names_to = "question", values_to = "lowest_response") |>
  mutate(floor_effect = ifelse(lowest_response > 0.3, "Yes", "No"))

#Distribution for questionnaire
qrp_distribution = qrp_data |> 
  select(anonym_id, qrp_attitude) |> 
  ggplot(aes(x = qrp_attitude)) +
  geom_bar() +
  coord_cartesian(xlim = c(8, 40))
```

# Checking correlation between variables to see redundancies

```{r}
cor_data = data |> 
  select(burnout:open_practice) |> 
  na.omit()

correlations <- cor(as.matrix(cor_data))
correlations[!lower.tri(correlations)] <- NA

correlations = data.frame(correlations) |> 
  rownames_to_column() |>
  gather(key="variable", value="correlation", -rowname)

correlations = correlations |> 
  mutate(above_.8 = abs(correlation) > 0.8) |> 
  filter(!is.na(correlation))

#Nothing is above 0.8 yet
```
